### 2018-09-15 Sections/foreword.tex
minor

The entirely technically disinterested or mathematically incompetent reader may refer to just Secs.~\ref{sec:introduction}, \ref{sec:outlook} \& \ref{sec:vision_quant} -- essentially brief non-technical, highly speculative essays about the motivation, applications and implications of the future quantum internet.

>>>>

The entirely technically disinterested or mathematically incompetent reader may refer to just Parts~\ref{part:introduction}, \ref{part:essays} \& \ref{part:the_end} -- essentially brief non-technical, highly speculative essays about the motivation, applications and implications of the future quantum internet.
